Title

### 2023-05-29 main.tex
Más cambios
Correcciones

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the state 
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}})
\label{eq:angle2} \\
\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
que quizá estén mas bonitas.}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}}
|00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
on them.
\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
a la ecuación.}
%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer\cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
la frase.}.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }
We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by 
\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
calculas. }

Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig: fidelity one qubit} the maximal probabilities of
success defined by \eref{eq: probability-success} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a low $p_{\succ}$, while those 
close to unitary channels have much higher $p_{\succ}$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

\begin{figure}
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.}}
\end{figure}

@@

In general, producing this curve of states for $N$ qubits will require
$2^N-1$ rotations parametrized by $p$\cpnote{De de donde sale este numero?},
such as the three rotations used for the ancilla
qubits in \fref{fig: circuit-pauli-1}.
However, it would be preferable to achieve the same effect using only one parametrized rotation. 
This would allow us to interpret said rotation 
as a knob that smoothly traverses the curve of states.
Consequently, we are faced with the question of which curves of states, 
such as the one described in \eref{eq: parametrized state}, 
can be produced using just a single parametrized rotation. 
To clarify this, we provide the following definition 
for a circuit with one parametrized rotation.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \left( \sqrt{1-3p/4}, \sqrt{p/4}, \sqrt{p/4},\sqrt{p/4} \right).
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle = e^{is} \left( \dfrac{1}{2}, \dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}} \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}}\right)
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $|a|^2 + |b|^2 + |c|^2 = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

>>>>

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\text{Ancilla state =} 
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
que quizá estén mas bonitas.}
\tbnote{Ya puse la puntuación y lo puse en términos de arctan.
La suma de arcotangentes se puede juntar en una 
sola arctan, pero con un argumento que ya queda muy complicado y 
creo que está mejor así.}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
a la ecuación.} \tbnote{Ya}
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

We took a sample of one-qubit Pauli channels and
used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
to simulate them. \cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
la frase.}
\tbnote{Ya.}  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }

\tbnote{Rediseño párrafo anterior: }
{\color{orange}  We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by}

%We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
%with the probability that one can distinguish two channels.
%In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
%with probability $1/2$ each,
%and tries to guess which channel they received
%by applying it to a state $\rho$ and measuring the result.
%Then, the maximal probability of success (out of all possible states $\rho$) that
%the agent guesses correctly is~\cite{Benenti}:
%\begin{equation}
%\label{eq: probability-success}
%p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
%\end{equation}
%where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by

\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
{\color{orange} The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.}
\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
calculas. } 
\tbnote{La calculo usando una función en la librería de Qiskit
que se basa en la referencia que puse,
pero la verdad no sé bien cómo funciona.}

%Notice that if the channels are the same, then $p_{\succ}=1/2$. 
%This is expected because in this situation the agent
%has no way of distinguishing the channels and has no choice but to completely
%guess, which results in a probability of success of $1/2$.
%On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
%distinguishable.
\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
\tbnote{Va, ya puse directo con la $f$ y quité lo de psucc}

{\color{orange} When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as:

\begin{align}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{align}
which is a number between $0$ and $1$,
with $1$ indicating that the channels are completely
equal and $0$ the opposite.
}
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

\begin{figure}
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.} Results of the diamond fidelities as defined in \eref{eq:diamond-fid} for a sample of Pauli channels in the tetrahedron.
Notice that channels close to the center of the tetrahedron have high fidelities,
while those close to the borders do not. 
Moreover, we show the results for cuts of the tetrahedron at different values of $\tau_3$.}
\label{fig:fids}
\end{figure}

@@

In general, producing this curve of states for $N$ qubits will require
many rotations parametrized by $p$,
such as the three rotations used for the ancilla
qubits in \fref{fig: circuit-pauli-1}.
However, it would be preferable to achieve the same effect using only one parametrized rotation. 
This would allow us to interpret said rotation 
as a knob that smoothly traverses the curve of states.
Consequently, we are faced with the question of which curves of states, 
such as the one described in \eref{eq: parametrized state}, 
can be produced using just a single parametrized rotation. 
To clarify this, we provide the following definition 
for a circuit with one parametrized rotation.

@@

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Then, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |0\rangle + \dfrac{1}{2} \sqrt{1-p^2} |1\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |2\rangle +  \dfrac{1}{2}(1+p) |3\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right),
\end{align*}
with $s = \arcsin(p)$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.
\end{itemize}

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $|a|^2 + |b|^2 + |c|^2 = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}
